---
title: "Interesting Forecasting Applications with R"
author: "Name Surname - esra nur tinaz"
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/home/baydogan/Courses/IE360/Guidelines/example_homework_0.Rmd",output_format="pdf_document")
rmarkdown::render("/home/baydogan/Courses/IE360/Guidelines/example_homework_0.Rmd",output_format="html_document")
```

1. [Time series forecasting using ARIMA models](https://blogs.oracle.com/datascience/introduction-to-forecasting-with-arima-in-r)

    This example is important because it introduces the forecasting methodology using ARIMA models in R. The steps are ...

2.[An overview of time series forecasting models](https://towardsdatascience.com/an-overview-of-time-series-forecasting-models-a2fa7a358fcb)
    this article defines main models for time series applications with using R and Phyton.
   
3. [What Makes ARIMA & XTS Objects So Useful for Forecasting
XTS Objects]
(https://datasciencelessons.com/2019/12/13/introduction-to-forecasting-with-arima-in-r/)

    an article about What Makes ARIMA & XTS Objects So Useful for Forecast
    
library(caTools)
sessionInfo()